``How Prolific Are You?": A Scientometric Analysis of Researchers

### 2018-11-22 paper/paper.tex
Finished first draft of paper

\section{Data}
The data contains 618 records of scholars with 25 attributes. There are no missing values, and eight of the attributes are integers. For ease of analysis, we have labeled the attributes as \textit{v1} through \textit{v25}. A sample of the data is shown in the Supplementary Materials section at the end of this paper.

@@

The variables we chose were \textit{v9} through \textit{v21} and \textit{v24}. \underline{maybe explain why these}. Again, we created a matrix of Pearson R correlations, and picked out those that were higher than 0.8. Figure 4 shows this result. \\

@@

Perhaps more interesting than the above results was when we plotted the maximum adjusted $R^2$ (without discarding any variables) against the number of predictor variables used (on this subset of the data). Figure 5 shows this result, where a logarithm function fits quite well to the data. The equation obtained was
\begin{equation}
	\text{Adj. } R^2 = 0.125465 \log n + 0.746654
\end{equation}

@@

\subsection{Cluster Analysis}
We next sought to cluster the points, as a first step towards identifying ``prolific" authors. Because finding the number of clusters in such high dimensional data is difficult, we chose to use two different algorithms--DBSCAN (Density-Based Spatial Clustering of Applications with Noise)\cite{ester1996density} and mean-shift clustering \cite{comaniciu2002mean}. We picked two subsets of the data to perform this analysis on--the first was the set of variables that were highly correlated with \textit{v4} (denote this subset as $S_1$)--we chose these because it had an especially high number of correlated variables--and the second was the subset discussed in the previous subsection (which we shall denote as $S_2$.

@@

>>>>

\section{Data}
The data contains 618 records of scholars with 25 attributes. There are no missing values, and eight of the attributes are integers. For ease of analysis, we have labeled the attributes as \textit{v1} through \textit{v25}. A table explaining what each of these variables are is given in Table 1 of the Supplementary Materials section at the end of this paper.

@@

The variables we chose were \textit{v9} through \textit{v21} and \textit{v24}. Again, we created a matrix of Pearson R correlations, and picked out those that were higher than 0.8. Figure 4 shows this result. \\

@@

Perhaps more interesting than the above results was when we plotted the maximum adjusted $R^2$ (without discarding any variables) against the number of predictor variables used (on this subset of the data). Figure 5 shows this result, where a logarithm function fits quite well to the data. This meets our intuition of ``diminishing returns" as we increase the number of predictor variables. The equation obtained was
\begin{equation}
	\text{Adj. } R^2 = 0.125465 \log n + 0.746654
\end{equation}

@@

\subsection{Cluster Analysis}
We next sought to cluster the points, as a first step towards identifying ``prolific" authors. Because finding the number of clusters in such high dimensional data is difficult, we chose to use two different algorithms--DBSCAN (Density-Based Spatial Clustering of Applications with Noise)\cite{ester1996density} and mean-shift clustering \cite{comaniciu2002mean} from Python's sklearn package \cite{scikit-learn}. We picked two subsets of the data to perform this analysis on--the first was the set of variables that were highly correlated with \textit{v4} (denote this subset as $S_1$)--we chose these because it had an especially high number of correlated variables--and the second was the subset discussed in the previous subsection (which we shall denote as $S_2$.

@@

\subsection{Identifying Prolific Authors}
Finally, we proceed to test our hypothesis--are the researchers in the individual clusters more ``prolific" than the others? For this, we used the results of the DBSCAN clustering because they were more succinct. We used the Welch's t-test \cite{welch1947generalization}, which does not assume equal variance between the two samples, and computed the p-values for all pairs of clusters (see Table 3 for the list of clusters) at 5\% and 10\% level of significance. Table 5 shows the results of this, where $C_1$ and $C_2$ are the cluster numbers.

Clearly, looking at the first and third rows, there is a statistically significant difference between the means of the individual clusters and the first two largest clusters. In the third row, the 13/14 variables were statistically significant at 95\% confidence level, the insignificant one being \textit{v24} (star count). We also looked at the ``goodness" of the clustering using the Silhouette score \cite{rousseeuw1987silhouettes}, which was 0.571. \cite{kaufman2009finding} notes that this value means that ``a reasonable structure has been found".\\

\begin{tabular}{|c|c|c|c|}
\hline 
$C_1$ & $C_2$ & \textbf{95\% significant} & \textbf{90\% significant} \\ 
\hline 
-1 & 0 & 1.0 & 1.0 \\ 
\hline 
-1 & 1 & 0.857 & 0.857 \\ 
\hline 
-1 & 2 & 0.928 & 1.0 \\ 
\hline 
0 & 1 & 0.786 & 0.857 \\ 
\hline 
0 & 2 & 1.0 & 1.0 \\ 
\hline 
1 & 2 & 0.643 & 0.786 \\ 
\hline 
\end{tabular} 
\begingroup
\captionof{table}{Percentage of significant Welch's test p-values at 95\% and 90\% confidence levels}
\endgroup
\hfill\break
